Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-21 tex/v3/section_5_numeric_expes.tex
update

Figure \ref{fig:margin_expe} summarizes the observed behaviors of both algorithms under these settings. We choose to only report results for $n=m=1000$ as we get similar findings for other values of $n$ and $m$.

\begin{figure*}[t]
	\begin{center}
		\includegraphics[width=5.25cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{12pt} 
		\includegraphics[width=5.25cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
		\includegraphics[width=5cm]{./figs/norm_M_time_toy_n1000}\hspace*{18pt}
		\includegraphics[width=5cm]{./figs/norm_M_div_toy_n1000}
	\end{center}
	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn for normalized cost matrix. Top panel: marginal violations as a function of the budget expressed as the decimation factor $n/n_b$. Bottom panel: (left) Running time gain and, (right) relative divergence variation. The results are averaged over 30 trials.} 
		\label{fig:margin_expe}
\end{figure*}
%
\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for "high" values of the regularization parameter $\eta$ ($\eta > 1$). The approximation quality diminishes for small $\eta$. As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge towards zero when increasing the budget of points. Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.  According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at low budget $n_b/n$ while the reverse holds when $n_b/n$ gets close to 1.  Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$. Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a close divergence $\inr{C, P}$ compared to Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.

>>>>

Figure \ref{fig:margin_expe} shows the behaviors of both algorithms under these settings and a normalized cost matrix. We choose to only report results for $n=m=1000$ as we get similar findings for other $n$ and $m$.

\begin{figure*}[t]
	\begin{center}
		\includegraphics[width=5.25cm]{./figs/norm_M_Mu_marginals_toy_n1000} \hspace*{12pt} 
		\includegraphics[width=5.25cm]{./figs/norm_M_Nu_marginals_toy_n1000} \\
		\includegraphics[width=5cm]{./figs/norm_M_time_toy_n1000}\hspace*{18pt}
		\includegraphics[width=5cm]{./figs/norm_M_div_toy_n1000}
	\end{center}
	\caption{Empirical evaluation of \emph{Screenkhorn} vs Sinkhorn. Top panel: marginal violations as a function of the budget expressed as the decimation factor $n/n_b$. Bottom panel: (left) Running time gain and, (right) relative divergence variation. The results are averaged over 30 trials} 
		\label{fig:margin_expe}
\end{figure*}
%
\emph{Screenkhorn} provides good approximation of the marginals $\mu$ and $\nu$ for "high" values of the regularization parameter $\eta$ ($\eta > 1$). The approximation quality diminishes for small $\eta$. As expected $\norm{{\mu} -{\mu}^{\text{sc}}}_1$ and $\norm{{\nu} -{\nu}^{\text{sc}}}_1$ converge towards zero when increasing the budget of points. Remarkably marginal violations are almost negligible whatever the budget for high $\eta$.  According to computation gain, \emph{Screenkhorn} is, up to 2 times, faster than Sinkhorn at high decimation factor $n/n_b$ while the reverse holds when $n_b/n$ gets close to 1.  Computational benefit of \emph{Screenkhorn} also depends on $\eta$ with appropriate values $\eta \leq 1$. Finally except for $\eta=0.1$ \emph{Screenkhorn} achieves a close divergence $\inr{C, P}$ compared to Sinkhorn showing that our static screening test does not harm Sinkhorn divergence.
